A Study of Common Bug Fix Patterns in Rust

### 2022-11-25 discussion.tex
move fixed

In this work, using Ruxanne we successfully mined 20 cross project bug fix patterns. We introduced these patterns in two groups: 12 general patterns and 8 BC-related patterns. Clippy is only able to detect four of the BC-related patterns. Fundamentally, Clippy cannot detect some of them. For instance, we proposed the pattern \textit{Adding mutability} which Clippy cannot detect, simply because it cannot predict the next change that the developer is going to make. To the best of our knowledge, the rest of the patterns cannot be reported by the current linting tools. We therefore believe that our work introduces a new direction for IDE tools to help Rust developers.

@@

We expected to obtain certain patterns regarding some certain Rust related features, such as \verb+move+, but our results did not include those patterns. Our speculation is that, since Rust has a strong compiler check before creating the program executable, the programmers usually get many errors, and they only push their code once it is free of compile errors. That is why, we think there are some patterns that were hidden from our sight.

>>>>

In this work, using Ruxanne we successfully mined 20 cross project bug fix patterns. We introduced these patterns in two groups: 12 general patterns and 8 BC-related patterns. Clippy is able to detect five of the BC-related patterns. Fundamentally, Clippy cannot detect some of them. For instance, we proposed the pattern \textit{Adding mutability} which Clippy cannot detect, simply because it cannot predict the next change that the developer is going to make. To the best of our knowledge, the rest of the patterns cannot be reported by the current linting tools. We therefore believe that our work introduces a new direction for IDE tools to help Rust developers.

@@

Furthermore, we expected to obtain some patterns associated with certain Rust-related features but our results did not include those patterns. Our speculation is that, since Rust has a strong compiler check before creating the program executable, the programmers usually get many errors, and they only push their code once it is free of compile errors. For instnace, we did not observe any patterns associated with \verb+move+ operator in Rust. This operator is used to transfer the ownership of values to a closure. In some cases (e.g. multithreading) not moving the ownership can create invalid references, something that Rust's compiler prevents. That is why we believe due to Rust's strong compiler check some patterns were hidden from our sight.
